At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.

### 2019-11-25 manuscript/reply_to_referees_2.tex

	18. Critique of manuscript structure [[not sure  how to address]]

		\begin{refquote}
			Results
			General: Please, do not include discussion in your results, it may confound readers.
		\end{refquote}

		\textbf{R:} Where, specifically, does the Referee feel that we have included discussion in our results? This vague and somewhat condescending feedback is not helpful.

	19. Incorrect claim that beginning of results is inaccurate [[done]]

@@

		\begin{refquote}
			Line 262. Your first sentence of results do not correspond with what follows. We will suggest you use most networks, or most herbivory networks and half pollination networks, or using the percentages you present in the discussion section.
		\end{refquote}

		\textbf{R:} This comment is in such poor English as to be nearly unintelligible. It is not clear whether the Referee is suggesting that we repeat our analyses using half of the pollination networks (without any clear reason as to why) or is simply confused about which analysis these results refer to. Since the Referee appears to have assumed that the within-family analyses are the \emph{only} analyses in the manuscript, the latter seems likely.

		Note that the results in lines XX-XX correspond to our first analysis: testing whether niche overlap decreases over increasing phylogenetic
		distance in a large dataset of pollination and herbivory networks. The overall regression did show that partner overlap decreases with increasing phylogenetic distance, so that more distantly-related plants are less likely to share interaction partners (see Fig. 1). The rest of this section gives more details about the differences between pollination and herbivory networks (lines XX-XX) and variation across networks (lines XX-XX), but note that none of these details change the overall regression. As this text is correct we have left it unchanged.

	20. Definition of community composition unclear [[done]]

@@

		\begin{refquote}
			Line 310. How was community composition measured? Is difficult to evaluate the quality of this result because you haven't described this methodology.
		\end{refquote}

		\textbf{R:} Community composition is the set of plant species that make up a community, as described by the researchers constructing each network. For tractability, we have summarized community composition as the number of species in each plant family. We have added text to the methods to state this more obviously.

		\begin{quotation}
			Next, we examined the connection between our network-level observations
		    and the number of species in each plant family present in each community.
		    Specifically, we tested the hypothesis that
		    varying relationships between phylogenetic distance and
		    pairwise niche overlap are due to the different distributions 
		    of families across networks. We defined the relationship between
		    phylogenetic distance and niche overlap as the change in 
		    log odds of two plants in a given network sharing an interaction 
		    partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
		    regression of niche overlap against phylogenetic distance within
		    a single network). We then related differences in this relationship
		    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
		    analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
	    \end{quotation}

	21. Confusion about permutation methodology [[done]]

@@

	21. Confusion about permutation methodology [[done]]

		\begin{refquote}
			Minor comments on Results
			297-298 You permuted interactions or phylogenetic distances?
		\end{refquote}

		\textbf{R:} As stated in the methods, we permuted interactions. Note that, in statistical terms, the two approaches are equivalent. We have rephrased the results to match the methods.

	22. Typo in Fig. 1 caption [[done]]

		\begin{refquote}
			Fig 1. "...the probability of a pair of plants sharing an interaction partner increased with increasing phylogenetic distance..." please, write decreased instead of increased.
		\end{refquote}

		\textbf{R:} We thank the Referee for pointing out this truly egregious typo, and have corrected it.

@@

		\textbf{R:} [[Check that caption states that min and max are very close together since permutation completely destroyed pattern.]]

	24. Confusion about line 328 [[done]]

		\begin{refquote}
			Line  328: "...increasing phylogenetic distance in 12...", what is 12? the number of families?
		\end{refquote}

		\textbf{R:} Yes, 12 is the number of families. We have revised the line to make this more explicit.

		In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families

	25. Complaints about table numbering and figure referencing [[done]]

@@

		\begin{refquote}
			Table number seem to be erroneous as you first mention table 2 and then table 1.

			\smallskip

			Figure 3 is only referenced in the text when talking about herbivory networks but not for pollination networks.
		\end{refquote}

		\textbf{R:} We have reordered the tables and added a redundant reference to Fig. 3.

@@

	\textbf{R:} We actually address the non-independence of trials (pairs of plants) by calculating $p$-values based on permutations of the observed networks (as opposed to assuming independent, binomially-distributed trials, which is certainly not the case). To emphasize our explanation of this, we have reordered the text and placed our discussion of the permutation methods under the sub-heading 'accounting for non-independence'. We hope that this will calm reader's worries about the validity of our conclusions.

4. Permuting the permuted networks is confusing [[done]]

	\begin{refquote}
		* Evaluating type I and type II errors: Permutations of permutations
		Paragraph p. 10, l. 187-197 is a bit confusing because of phrasings such as “permutations/permuting of the permuted networks”. I don't have a better way to name this second round of permutations, but the overall is difficult to follow and could be shortened while still conveying the same message.
		Actually, I find the comment in Supplementary information 3 clearer, although no reference to Supplementary information 3 is made.
		Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig. 2, thin lines indicating 
		extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.
	\end{refquote}

	\textbf{R:} We agree with the Referee about the difficulty of describing this procedure. We have added an extra line to further explain the logic behind the second round of permutations and hope that this will clarify the goal of these analyses. We have also added a reference to Supplementary Information 3 and thank the Referee for pointing out the oversight.

	\begin{quotation}
		This permutation approach also allows us to estimate type I and type II 
	    error for our analysis. Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
	\end{quotation}

@@

	\textbf{R:} Umm... what does this mean? [[Probably going to go with "beyond the scope"]]

6. Request for consideration of multiple testing

	\begin{refquote}
		* Testing within-family existence of a phylogenetic signal
		Examining the strength of phylogenetic signal within plant families is an interesting idea. However, this leads to multiple testing which is prone to type I errors and I could not find mention of correction for this multiple testing in the text. There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)^N = 0.36 and 0.91 respectively, alpha = 0.05). Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).
	\end{refquote}

	\textbf{R:} [[Wasn't this the point of looking at type I errors? Or something?]] [[maybe we talk about this in the discussion?]][[Or I can compare to the permuted networks?]]

@@

14. Rephrasing of permutation strategy confusing [[done]]

	\begin{refquote}
		p. 14, l. 297-298 “Comparing the results in the observed networks with those obtained after permuting phylogenetic distances across pairs of plants (...)”: In the methods, interactions are shuffled, not phylogenetic distances. Doing one of the other seems equivalent for this test, but this rephrasing is a bit confusing.
	\end{refquote}

	\textbf{R:} We thank the Referee for pointing out this rephrasing, and have corrected the results to read the same as the methods.

@@

	Lines XX-XX:
	\begin{quotation}
		More closely-related plants in pollination networks did, however, tend to share fewer interaction partners ($\beta_{pollination}$=-0.776, $p$=0.007), similar to our within-network results above.
	\end{quotation}

16. Fig. 3, Table 2 conflict for Poaceae [[done]]

	\begin{refquote}
		Legend of Fig. 3 “(…) Melastomatoaceae and Poaceae in pollination networks are not significantly different from zero.” but Table 2 shows the opposite for Poaceae.
	\end{refquote}

	\textbf{R:} We thank the Referee for pointing out this error. The table is correct, and the change in log odds for \emph{Poaceae} in pollination networks was significant. We have corrected the legend of Fig. 3.

17. A confusing attempt at subtelty [[done]]

	\begin{refquote}
		In the figures, $\beta_{distance}$ is alternatively named “slope of regression line” (Fig. 2) and “change in log odds” (Fig. 3).
	\end{refquote}

	\textbf{R:} $\beta_{distance}$ is both the slope of the regression line \emph{and} the change in log odds of a pair of plants sharing a partner as distance increases. We wanted to include both interpretations to help readers relate the regressions to what is happening ecologically. However, we can see how having the different interpretations isolated in different figures could be confusing. We have therefore added parenthetical definitions in both captions to make it clear that Fig. 2 and Fig. 3 are referring to the same quantity.

### 2019-11-25 manuscript/phylogenetic_signal_manuscript.tex
more corrections. Nearly done with R4

      This permutation approach also allows us to estimate type I and type II 
      error for our analysis. To do this, we created 500 permutations of each 
      permuted network and, again keeping the observed phylogenetic distances 
      between plant species, repeated our analyses. We can then determine the 
      number of permuted networks which appear to have significant 
      overlap-phylogenetic distance relationships relative to the permutations 
      of these permuted networks (type I error). Type II error can be determined
      from the distribution of p-values obtained when comparing the permuted 
      networks to permutations of the permuted networks. Although calculating 
      the exact type II error requires a specific alternative hypothesis, the 
      uniform distribution of p-values we obtained after permuting the permuted 
      networks means that the type II error would increase linearly as the 
      alternative hypothesis was set farther from zero.

@@

    Next, we examined the connection between our network-level observations
    and the plant families present in each community.
    Specifically, we tested the hypothesis that
    varying relationships between phylogenetic distance and
    pairwise niche overlap are due to the different distributions 
    of families across networks. We defined the relationship between
    phylogenetic distance and niche overlap as the change in 
    log odds of two plants in a given network sharing an interaction 
    partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
    regression of niche overlap against phylogenetic distance within
    a single network). We then related differences in this relationship
    to differences in the composition of the plant community in each
    network using a non-parametric permutational multi-variate 
    analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
    As we did not wish to inflate the perceived similarity between
    pairs of networks which did not include many of the same families,
    we used Bray-Curtis dissimilarity to define differences in plant
    community composition. Bray-Curtis dissimilarity considers only
    those plant families which appear in at least one of a pair of
    networks~\citep{Anderson2001,Cirtwill2015}, ensuring that the
    shared absence of rare plant families will not make 
    two networks appear more similar than they actually are.

@@

    Comparing the results in the observed networks to those obtained after 
    permuting phylogenetic distances across pairs of plants, the observed 
    slope of the relationship between phylogenetic distance and interaction 
    partner overlap was always more extreme (i.e., always more negative or 
    always more positive) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
    Observed networks with a negative relationship between phylogenetic distance 
    and overlap always had a more negative slope than that obtained from the 
    permuted networks, while the 10 networks with positive relationships 
    between phylogenetic distance and overlap always had more positive 
    relationships than the permuted networks. This suggests that even in 
    the networks with non-significant relationships, the association between niche overlap and 
    phylogenetic distance was not random. When the slopes of the permuted 
    networks were compared to those obtained from permutations of the 
    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 3}).

@@

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    For the 48 families that were well represented in pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 (Table~\ref{family_slopes_pp}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 34 plant families (see \emph{Supporting information 4} for further 
    details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[width=.5\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
    \end{center}
     \caption{Results of a mixed-effects logistic regression of pairwise niche overlap
     against phylogenetic distance for plants in 11
     herbivory networks (top; green) and 59 pollination
     networks (bottom; purple). In both network types, the probability of a pair of plants
     sharing an interaction partner increased with increasing phylogenetic distance (thick,
     dark lines). There was substantial variation among networks (thin, pale lines) of both types. The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10^{-13}$).}
    \label{within_network_regression} 
  \end{figure}

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
    \end{center}
     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network. Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks. Thick, dashed lines represent the mean slopes across all networks of each type. The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines. For both network types, the slopes obtained from permuted networks were always very close to 0.}
    \label{obs_vs_random} 
  \end{figure}

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
    \end{center}
    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore as phylogenetic distance between the plants increases. These values are analogous to the slopes of the regression lines from Eq. 2-3 and represent
    the change in the probability of observing shared 
    interaction partners per million years of divergence time. 
    For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type. 
    Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} and \emph{Poaceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types. All other plant families were well-represented in only one network type.
    Families in pollination networks are indicated
    by dark purple diamonds while families in herbivory
    networks are indicated by pale green circles.
    We also
    show the slope of the relationship between the
    log-odds of observing each overlap pattern and 
    phylogenetic distance across all plant families
    in herbivory (pale, green horizontal line) and
    pollination (dark, purple horizontal line) networks.
    The phylogenetic tree below the plots indicates the
    relatedness between these plant families. Error bars represent 95\% 
    confidence intervals.}
    \label{within_family_regression}
  \end{figure}

>>>>

      This permutation approach also allows us to estimate type I and type II 
      error for our analysis. Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.
      To estimate type I and type II errors, we created 500 permutations of each 
      permuted network and, again keeping the observed phylogenetic distances 
      between plant species, repeated our analyses. We could then determine the 
      number of permuted networks which appear to have significant 
      overlap-phylogenetic distance relationships relative to the permutations 
      of these permuted networks (type I error). Type II error can be determined
      from the distribution of p-values obtained when comparing the permuted 
      networks to permutations of the permuted networks. Although calculating 
      the exact type II error requires a specific alternative hypothesis, the 
      uniform distribution of p-values we obtained after permuting the permuted 
      networks means that the type II error would increase linearly as the 
      alternative hypothesis was set farther from zero (\emph{Supporting Information 3}).

@@

    Next, we examined the connection between our network-level observations
    and the number of species in each plant family present in each community.
    Specifically, we tested the hypothesis that
    varying relationships between phylogenetic distance and
    pairwise niche overlap are due to the different distributions 
    of families across networks. We defined the relationship between
    phylogenetic distance and niche overlap as the change in 
    log odds of two plants in a given network sharing an interaction 
    partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
    regression of niche overlap against phylogenetic distance within
    a single network). We then related differences in this relationship
    to differences in the composition of the plant community (defined as the number of species in each plant family present in each network) using a non-parametric permutational multi-variate 
    analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
    As we did not wish to inflate the perceived similarity between
    pairs of networks which did not include many of the same families,
    we used Bray-Curtis dissimilarity to define differences in plant
    community composition. Bray-Curtis dissimilarity considers only
    those plant families which appear in at least one of a pair of
    networks~\citep{Anderson2001,Cirtwill2015}, ensuring that the
    shared absence of rare plant families will not make 
    two networks appear more similar than they actually are.

@@

    Comparing the results in the observed networks to those obtained after 
    permuting interactions, the observed 
    slope of the relationship between phylogenetic distance and interaction 
    partner overlap was always more extreme (i.e., always more negative or 
    always more positive) than that obtained in the permuted networks (Fig.~\ref{obs_vs_random}).
    Observed networks with a negative relationship between phylogenetic distance 
    and overlap always had a more negative slope than that obtained from the 
    permuted networks, while the 10 networks with positive relationships 
    between phylogenetic distance and overlap always had more positive 
    relationships than the permuted networks. This suggests that even in 
    the networks with non-significant relationships, the association between niche overlap and 
    phylogenetic distance was not random. When the slopes of the permuted 
    networks were compared to those obtained from permutations of the 
    permuted networks, there was no relationship, which speaks to the robustness of our methodology (\emph{Supporting information 3}).

@@

    Considering each family separately, the relationship between within-family niche overlap and phylogenetic distance varied widely in both pollination and herbivory networks. 
    In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 12 of the 48 well-represented families (Table~\ref{family_slopes_pp}; Fig.~\ref{within_family_regression}).
    There was no significant relationship between overlap and phylogenetic distance in
    a further 34 plant families (see \emph{Supporting information 4} for further 
    details). Finally, the overlap between pairs of \emph{Apiaceae} and \emph{Poaceae} increased significantly with increasing phylogenetic distance.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[width=.5\textwidth]{Figures/dataplots/scaled_regression_lines_full_color.eps}}
    \end{center}
     \caption{Results of a mixed-effects logistic regression of pairwise niche overlap
     against phylogenetic distance for plants in 11
     herbivory networks (top; green) and 59 pollination
     networks (bottom; purple). In both network types, the probability of a pair of plants
     sharing an interaction partner decreased with increasing phylogenetic distance (thick,
     dark lines). There was substantial variation among networks (thin, pale lines) of both types. The slope of the regression for each network was significantly more extreme than that obtained from 999 permutatations of that network (slopes obtained from the permuted networks ranged between -1.34$\times10^{-12}$ and 9.19$\times10^{-13}$).}
    \label{within_network_regression} 
  \end{figure}

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
    \end{center}
     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance (representing the change in log odds of a pair of plants sharing an interaction partner) was signficantly different from 0 for each network. Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks. Thick, dashed lines represent the mean slopes across all networks of each type. The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines. For both network types, the slopes obtained from permuted networks were always very close to 0.}
    \label{obs_vs_random} 
  \end{figure}

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.62\textheight]{Figures/dataplots/Family/allfams_full.eps}}
    \end{center}
    \caption{Change in the log odds of a pair of plants sharing a pollinator or herbivore (i.e., the slopes of the mixed-effect logistic regressions) as phylogenetic distance between the plants increases. These values are analogous to the slopes of the regression lines from Eq. 2-3 and represent
    the change in the probability of observing shared 
    interaction partners per million years of divergence time. 
    For clarity, we show only the 15 plant families for which the slope of the regression of the proportion of shared interaction partners against phylogenetic distance was significant in at least one network type. 
    Note that the change in log odds for \emph{Asteraceae} in herbivory networks and \emph{Melastomataceae} in pollination networks are not significantly different from zero; we present these values only for comparison across network types. All other plant families were well-represented in only one network type.
    Families in pollination networks are indicated
    by dark purple diamonds while families in herbivory
    networks are indicated by pale green circles.
    We also
    show the slope of the relationship between the
    log-odds of observing each overlap pattern and 
    phylogenetic distance across all plant families
    in herbivory (pale, green horizontal line) and
    pollination (dark, purple horizontal line) networks.
    The phylogenetic tree below the plots indicates the
    relatedness between these plant families. Error bars represent 95\% 
    confidence intervals.}
    \label{within_family_regression}
  \end{figure}
